Web feed based content extraction with JavaScript rendering for the Invenio crawler

### 2013-10-29 tex/5-evaluation.tex
Extract the dataset blog contents and urls, included last suggestion from vangelis.
Move dataset to /dataset.

\subsection{Introcution}
What is evaluated (not comments, iframes, authors, dates...)

\subsection{Content extraction}
Compare:
\begin{itemize}
  \item Our solution
  \item Boilerpipe \surl{https://github.com/misja/python-boilerpipe}
  \item Goose \surl{https://github.com/grangier/python-goose}
  \item Readability \surl{https://github.com/buriy/python-readability}
\end{itemize}
On:
\begin{enumerate}
  \item Running time
  \begin{itemize}
    \item Plot duration as a function of the page length
    \item Plot duration as a function of the number or pages (our should only take time to build the rules)
  \end{itemize}
  \item Quality of output compared:
  \begin{itemize}
    \item Chart of success pourcentages
  \end{itemize}
\end{enumerate}

>>>>

\subsection{Introcution}
What is evaluated (not comments, iframes, authors, dates...)
\\ define the dataset and your competing algorithms the best way possible.

The dataset is a small sample coming from the Spinn3r dataset. The Spinn3r dataset was released for ICWSM 2011 conference.

\subsection{Content extraction}
Compare:
\begin{itemize}
  \item Our solution
  \item Boilerpipe q\surl{https://github.com/misja/python-boilerpipe}
  \item Goose \surl{https://github.com/grangier/python-goose}
  \item Readability \surl{https://github.com/buriy/python-readability}
\end{itemize}
On:
\begin{enumerate}
  \item Running time
  \begin{itemize}
    \item Plot duration as a function of the page length
    \item Plot duration as a function of the number or pages (our should only take time to build the rules)
  \end{itemize}
  \item Quality of output compared:
  \begin{itemize}
    \item Chart of success pourcentages
  \end{itemize}
\end{enumerate}
